---
title: "Abalone Report"
author: "Melinda Higgins"
date: "January 27, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(warnings = FALSE)
knitr::opts_chunk$set(message = FALSE)

library(dplyr)
library(ggplot2)
library(readr)
library(psych)
```

## Abalones

For this exercise, we will be working with a dataset on abalones available from the UC Irvine Machine Learning Repository at [https://archive.ics.uci.edu/ml/datasets/abalone](https://archive.ics.uci.edu/ml/datasets/abalone). The dataset can be downloaded from the **Data Folder** and the details about the dataset can be read in the **Data Set Description**.

```{r}
abalone <- readr::read_csv(file = "abalone.csv")

# abalone <- abalone %>% 
#   filter(sex == "M")
```

## Inline Code

We can computer statistics on the fly and include them in the body of the text. For example, the mean and standard deviation of the abalone whole weight is `r round(mean(abalone$wholeWeight), digits=2)`(`r round(sd(abalone$wholeWeight), digits=2)`).

## Summary statistics numeric measurements

```{r}
t <- abalone %>%
  select(-sex) %>%
  psych::describe()
knitr::kable(t)
```

## Make a scatterplot of abalone measurements

```{r}
ggplot(abalone, aes(x = wholeWeight, y = rings)) +
  geom_point(aes(color = sex)) +
  ggtitle("Abalone Rings by Whole Weight by Sex")
```

